\huge Modeling Intervention Strategies for TB Control in the United States

### 2013-07-27 in_progress/presentations/poster/reuMHC2013.tex
working on poster intro

\begin{frame}
  \begin{columns}
    \begin{column}{.3\textwidth}
%      \begin{block}{Introduction}
%        The most common epidemiological models are compartmental models, in
%        which a system of differential equations describes how parts of the
%        population move between different disease states, or
%        \emph{compartments}. The canonical example of such a model is the SIR
%        model, which has three compartments: Susceptible, Infected, and
%        Recovered. The dynamics of a population modeled by this framework are
%        shown in figure~\ref{fig:SIRFlowchart}, with associated system of
%        differential equations~\ref{eq:SIRdes}.
        %TODO equalize figure heights
%        \vspace{-3em}
%        \begin{block}{}
%          \begin{column}{.39\textwidth}
%            \begin{figure}[h]
%              \begin{center}
%                \begin{tikzpicture}
%                  \node [compartment] (S) {Susceptible (S)};
%                  \node [compartment, below of=S] (I) {Infected (I)};
%                  \node [compartment, below of=I] (R) {Recovered (R)};
%                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
%                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
%                \end{tikzpicture}
%              \end{center}
%              \caption{This flowchart depicts the standard SIR epidemiological
%                       model. It is accomponanied by the system of differential
%                       equations~\ref{eq:SIRdes}.}
%              \label{fig:SIRFlowchart}
%            \end{figure}
%          \end{column}
%          \begin{column}{.39\textwidth}
%            \begin{figure}[h]
%              \begin{align*}
%                \frac{dS}{dt} &= -\beta S(t)I(t) \\
%                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
%                \frac{dR}{dt} &= \gamma I(t)\\
%                N             &= S(t) + I(t) + R(t)\\
%              \end{align*}
%              \caption{The system of differential equations governing the SIR
%                       model.}
%              \label{eq:SIRdes}
%            \end{figure}
%          \end{column}
%        \end{block}
%        The SIR system, though very informative about basic disease dynamics,
%        fails to capture the intricacies of more complicated diseases. This
%        project examines the spread of tuberculosis (TB) in the United States
%        (US) via compartmental models and stochastic, agent-based models. These
%        explorations allow one to explore the impact, both epidemiological and
%        economic, of various intervention strategies. These models are based on
%        a 2012 compartmental model of TB in the US created by A. N. Hill, J. E.
%        Becerra, and K. G. Castro.
%      \end{block}

      \begin{block}{The Basic Hill Model}
        \begin{block}{}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[scale=.75]{HillModelFlowChart}
              \end{center}
              \caption{A flow chart representing the compartments of the Hill
                       Model.}
              \label{fig:hillFlow}
            \end{figure}
        \end{block}
%            The illustration of this model is not full, as there are two
%            subpopulations in the Hill Model. TB dynamics in the US differ
%            radically between US born (USB) individuals and foreign born (FB)
%            individuals,  so this model maintains two distinct populations in
%            which the disease can spread. There is a near identical diagram to
%            describe the dynamics of the model for the FB population. Further,
%            each compartment in this model also loses people to do natural
%            death. The system of differential equations for this model is
%            naturally more complex and is provided in an appendix. In order to
%            implement this model, Hill, Becerra, and Castro used the \texttt{R}
%            programming language, with the \texttt{lsoda} routine to numerically
%            solve the differential equations.

        For this implementation, various numerical solvers were implemented,
        including an Eulerian Method, a Quadratic Method, a Fourth-order runge
        kutta method, and the $\texttt{lsoda}$ routine. Once the basic Hill
        model was implemented, further tracking capabilities were added as well
        as economic modeling. This implementation tracks total active TB cases,
        entering cases of LTBI, and treatment costs for active and latent disease
        for all populations. Tracking was used to evaluate various interventions
        explored in Hill, Becerra, and Castro's work, as well as interventions
        exploring the possibility of treating incoming LTBI cases.
      \end{block}
    \end{column}

>>>>

\begin{frame}
  \begin{columns}
    \begin{column}{.3\textwidth}
      \vspace{-8em}
      \begin{block}{Introduction}
        Epidemiological models offer insight into the structure of disease
        outbreaks and the merits of various interventions. The most common
        epidemiological models are compartmental differential equation models,
        such as the SIR system, illustrated in figures~\ref{fig:SIRFlowchart}
        and~\ref{eq:SIRdes}. 
       %TODO equalize figure heights
        \vspace{-2em}
        \begin{block}{}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{center}
                \begin{tikzpicture}
                  \node [compartment] (S) {Susceptible (S)};
                  \node [compartment, below of=S] (I) {Infected (I)};
                  \node [compartment, below of=I] (R) {Recovered (R)};
                  \path [line] (S) -- node [compartment rate] {$\beta S(t)I(t)$} (I);
                  \path [line] (I) -- node [compartment rate] {$\gamma I(t)$} (R);
                \end{tikzpicture}
              \end{center}
              \caption{This flowchart depicts the standard SIR epidemiological
                       model. It is accomponanied by the system of differential
                       equations~\ref{eq:SIRdes}.}
              \label{fig:SIRFlowchart}
            \end{figure}
          \end{column}
          \begin{column}{.39\textwidth}
            \begin{figure}[h]
              \begin{align*}
                \frac{dS}{dt} &= -\beta S(t)I(t) \\
                \frac{dI}{dt} &= \beta S(t)I(t) - \gamma I(t) \\
                \frac{dR}{dt} &= \gamma I(t)\\
                N             &= S(t) + I(t) + R(t)\\
              \end{align*}
              \caption{The system of differential equations governing the SIR
                       model.}
              \label{eq:SIRdes}
            \end{figure}
          \end{column}
        \end{block}
      \end{block}

      \begin{block}{The Basic Hill Model}
        In order to model tuberculosis (TB) in the United States (US), Hill,
        Becerra, and Castro designed a complex compartmental model called the
        hill model. 
        \vspace{-2em}
        \begin{block}{}
          \begin{column}{.6\textwidth}
            \begin{figure}[h]
              \begin{center}
                \includegraphics[scale=.5]{HillModelFlowChart}
              \end{center}
              \caption{A flow chart representing the compartments of the Hill
                       Model.}
              \label{fig:hillFlow}
            \end{figure}
          \end{column}
          \begin{column}{.33\textwidth}
            Populations:
            \begin{itemize}
              \item US Born Individuals (USB) 
              \item Foreign Born Individuals (FB)
            \end{itemize}
            Individuals also leave the model due to natural death.
          \end{column}
        \end{block}
        %For this implementation, various numerical solvers were implemented,
        %including an Eulerian Method, a Quadratic Method, a Fourth-order runge
        %kutta method, and the $\texttt{lsoda}$ routine. Once the basic Hill
        %model was implemented, further tracking capabilities were added as well
        %as economic modeling. This implementation tracks total active TB cases,
        %entering cases of LTBI, and treatment costs for active and latent disease
        %for all populations. Tracking was used to evaluate various interventions
        %explored in Hill, Becerra, and Castro's work, as well as interventions
        %exploring the possibility of treating incoming LTBI cases.
      \end{block}
    \end{column}
